\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-08-14 doc/sw-system.tex
Initial PL/PD symbols used - to match ROC curve plot legend

We conservatively initialize both elements of each  agent's confusion
matrix to be 0.5, that of a maximally ambivalent  random classifier, so
that all agents start with zero skill. While  this makes no allowance
for volunteers that actually do have previous experience of what
gravitational lenses look like, we might expect it to help mitigate
against false positives. Anyone who classifies more than one image (by
progressing beyond the tutorial) makes a non-zero information
contribution to the project.

>>>>

We conservatively initialize both elements of each  agent's confusion
matrix to be $\CM^0_{LL} = \CM^0_{NN} = 0.5$, that of a maximally ambivalent  random classifier, so
that all agents start with zero skill. While  this makes no allowance
for volunteers that actually do have previous experience of what
gravitational lenses look like, we might expect it to help mitigate
against false positives. Anyone who classifies more than one image (by
progressing beyond the tutorial) makes a non-zero information
contribution to the project.
